Untrusted B2B Collaboration using the Blockchain

### 2018-07-25 paper/paper.tex
clarify per-company-setup

%TODO add a step where other factory contracts are set
Each organization needs to perform some setup before they can take part in a process execution.
An access contract and a factory contract for a process need to be deployed, if it has not been done yet.
Additionally, the user-to-role and and task-to-role mappings have to be updated, to allow verification of users during the process execution.
A diagram of this process can be seen in Figure \ref{fig:initialization}.

>>>>

%TODO add a step where other factory contracts are set
Each organization needs to perform some setup before they can take part in a process execution.
An access contract and a factory contract for a process need to be deployed, if it has not been done yet.
Additionally, the user-to-role and and task-to-role mappings have to be updated (via the \emph{giveRights} and \emph{assignRole} functions), to allow verification of users during the process execution.
A diagram of this process can be seen in Figure \ref{fig:initialization}.
